A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
Add more things to the paper

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}

@@

Cache

@@

We attempted to measure the

>>>>

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[11pt]{article}
\usepackage[pdftex]{graphicx}

@@

After implementation and profiling, we found that dictionary table lookups had
over twice as many level 1 cache misses with tabulation hashing than without.
Hypothesizing that the tabulation tables were evicting other, more relavant
data from the level 1 cache.  To fix this, we inserted x86 memory prefetch
instructions into our hash code to tell the CPU's caching system that it should
deprioritize storing it in cache.  We used GCC's
\begin{tt}\_\_builtin\_prefetch(void \*addr, char rw, char locality)\end{tt}
to do this.  However, this only yielded about a 1\% performance improvement.

@@

We attempted to measure the 
See Figure ~\ref{fig:tables}
 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{tables.pdf}
   \caption{}
   \label{fig:tables}
 \end{figure}
